### 2012-02-08 trunk/GUIErrorDetector/paper/evaluation.tex
tweak and make the cg larger

We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
more errors with fewer false positive warnings than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph, and may
mix the same method calls by different callers into a single node, thus
introducing imprecision. Although the error-revealing paths exist in
less precise graphs, the impreicison prevents our algorithm finding them.
Figure~\ref{fig:ex} illustrates this limitation.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.33]{cgexample}
  \vspace*{-3.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
\CodeIn{safeMtd()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA. Nodes for constructors and \CodeIn{Thread.run()}
are omitted for brevity. Using the less precise call graph, the error
detection algorithm will report an invalid method call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()},
but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()}. The
actual error path can only be found when using the more precise call graph.
}}
\end{figure}

@@

The first variant uses DFS for graph traversal by changing
line 8 in Figure~\ref{fig:detectalgorithm} to:
$\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
and changing queue operations (\CodeIn{enqueueAll}, and \CodeIn{dequeue}
on lines 9, 12, and
23 in Figure~\ref{fig:androiderror}, respectively)
to the corresponding statck operations (\CodeIn{pushAll}, and \CodeIn{pop}).
This variant found 11 errors in total and missed 1 error in the FileBunker subject.
The reason is that DFS tends to search deeper into the graph, and the path it returns
may not be the shortest one and is more likely to be an infeasible path in practice.
%For the FileBunker subject, paths
%returned by DFS are much longer than BFS, and do not actually exist.

>>>>

We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
more errors with fewer false positive warnings than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph, and may
mix the same method calls by different callers into a single node, thus
introducing imprecision. Although the error-revealing paths exist in
less precise graphs, the impreicison prevents our algorithm finding them.
Figure~\ref{fig:ex} illustrates this point.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.45]{cgexample}
  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
Using the less precise call graph, the error
detection algorithm will report an invalid method call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
$\rightarrow$ \CodeIn{uiAcc()},
but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}. The
actual error path can only be found when using the more precise call graph.
}}
\end{figure}

@@

The first variant uses DFS for graph traversal by changing
line 8 in Figure~\ref{fig:detectalgorithm} to:
$\mathit{worklist}$ $\leftarrow$ $\mathit{an}$ $\mathit{empty}$ $\mathit{stack}$,
and changing queue operations (\CodeIn{enqueueAll}, and \CodeIn{dequeue}
on lines 9, 12, and
23 in Figure~\ref{fig:detectalgorithm}, respectively)
to the corresponding statck operations (\CodeIn{pushAll}, and \CodeIn{pop}).
This variant found 11 errors in total and missed 1 error in the FileBunker subject.
The reason is that DFS tends to search deeper into the graph, and the path it returns
may not be the shortest one and is more likely to be an infeasible path in practice.
%For the FileBunker subject, paths
%returned by DFS are much longer than BFS, and do not actually exist.

### 2012-02-08 trunk/GUIErrorDetector/paper/introduction.tex
update the experimental data
tweak and make the cg larger

\begin{figure}[t]
\hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \{
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \}
\end{alltt}
\end{CodeOut}
\hspace{6mm} \small{In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \{
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \}
\end{alltt}
\end{CodeOut}
 \hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \}
\end{alltt}
\end{CodeOut}
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222,
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} %\vspace{-5mm}
\end{figure}

@@

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
   org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
-> android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)
-> java.lang.Thread.start()
-> android.opengl.GLSurfaceView\$GLThread.run()
-> android.opengl.GLSurfaceView\$GLThread.guardedRun()
-> org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)
-> org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)
   ... 
-> android.view.ViewRoot.recomputeViewAttributes(View;)
-> android.view.ViewRoot.checkThread()
\end{alltt}
\end{CodeOut}
%\hspace{5mm}\CodeIn{\scriptsize{org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{java.lang.Thread.start()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.run()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.guardedRun()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)}}\\
%\hspace{5mm}\CodeIn{...}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
\vspace*{-3.0ex} \Caption{{\label{fig:report} Our tool reports
a method call chain that reveals the potential error in
Figure~\ref{fig:androiderror}. $\rightarrow$ represents
the call relationship
between methods, and \CodeIn{checkThread} is an Android library
method  that checks whether the current thread is the
event dispatching thread before accessing a GUI object.
8 more methods in the call chain, shown as
\CodeIn{\small{...}} above, are omitted for brevity.
}} %\vspace{-5mm}
\end{figure}

Our static analysis formulates finding invalid thread access as a call graph reachability
problem. Given a call graph, our technique traverses
every possible path from its entry nodes, checking whether
any path accesses a GUI object from a non-UI thread. If 
a suspicious path is found, the static analysis warns of a potential error.
The warning is in the form of a method
call chain from the starting point.
As an example, Figure~\ref{fig:report} shows a report produced
by our static analysis for the buggy code in Figure~\ref{fig:androiderror}.
This report clearly indicates how a new, non-UI thread is spawned and
accesses GUI objects. The generated report allows  developers to
inspect the method call chain, understand how the error
could be triggered, and fix it if it is a real bug.

Our static analysis is independent of the call graph construction algorithm.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. GUI applications tend to use reflection, and
in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a good call graph.
To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
also compare its usefulness with existing call graph construction algorithms in
our experiments. Static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To address such limitations, we devise a set
 of sound and heuristic filters to remove likely false positives and redundant warnings.

@@

Our tool works in a fully automatic, push-button manner,
and scales to realistic programs.
We evaluated our implementation on \subnum programs comprising over \totaloc LOC.
The experiment results demonstrate
that: our technique is effective (it found \bugs real-world errors
from four supported frameworks and produced only \falses false positive warnings);
our reflection-aware call graph construction algorithm helps in
finding errors in Android applications;
and our proposed filters significantly reduce the number of
false positives and redundant warnings.

@@

\item \textbf{Evaluation.} We applied our tool to \subnum programs 
from 4 different frameworks, comprising over \totaloc LOC. The results
show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).

>>>>

\begin{figure}[t]
\hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \{
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \}
\end{alltt}
\end{CodeOut}
\hspace{6mm} \small{In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \{
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \}
\end{alltt}
\end{CodeOut}
 \hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \}
\end{alltt}
\end{CodeOut}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222,
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} %\vspace{-5mm}
\end{figure}

@@

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
   org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
-> android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)
-> java.lang.Thread.start()
-> android.opengl.GLSurfaceView\$GLThread.run()
-> android.opengl.GLSurfaceView\$GLThread.guardedRun()
-> org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)
-> org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)
   ... 
-> android.view.ViewRoot.recomputeViewAttributes(View;)
-> android.view.ViewRoot.checkThread()
\end{alltt}
\end{CodeOut}
%\hspace{5mm}\CodeIn{\scriptsize{org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{java.lang.Thread.start()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.run()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.guardedRun()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)}}\\
%\hspace{5mm}\CodeIn{...}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:report} Our tool reports
a method call chain that reveals the potential error in
Figure~\ref{fig:androiderror}. $\rightarrow$ represents
the call relationship
between methods, and \CodeIn{checkThread} is an Android library
method  that checks whether the current thread is the
event dispatching thread before accessing a GUI object.
8 more methods in the call chain, shown as
\CodeIn{\small{...}} above, are omitted for brevity.
}} %\vspace{-5mm}
\end{figure}

Our static analysis formulates finding invalid thread access as a call graph reachability
problem. Given a call graph, our technique traverses
paths from its entry nodes, checking whether
any path accesses a GUI object from a non-UI thread. If 
a suspicious path is found, the static analysis warns of a potential error.
The warning is in the form of a method
call chain from the starting point.
As an example, Figure~\ref{fig:report} shows a report produced
by our static analysis for the buggy code in Figure~\ref{fig:androiderror}.
This report clearly indicates how a new, non-UI thread is spawned and
accesses GUI objects. The generated report allows  developers to
inspect the method call chain, understand how the error
could be triggered, and fix it if it is a real bug.

Our static analysis is independent of the call graph construction algorithm.
Given a sound call graph, our analysis is sound in that it does
not miss true positives. GUI applications tend to use reflection, and
in the presence of reflection, existing call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a good call graph.
To alleviate this problem, we present an algorithm to build reflection-aware call graph, and
also compare its usefulness with existing call graph construction algorithms in
our experiments. Static analysis may report false positives due to its
conservative nature, or multiple warnings that actually correspond
to the same error. To address such limitations, we devise a set
 of error filters to remove likely false positives and redundant warnings.

@@

Our tool works in a fully automatic, push-button manner,
and scales to realistic programs.
We evaluated our implementation on \subnum programs comprising \totaloc LOC.
The experiment results demonstrate
that: our technique is effective (it found \bugs real-world errors
from four supported frameworks and produced only \falses false positive warnings);
our reflection-aware call graph construction algorithm helps in
finding errors in Android applications;
and our proposed filters significantly reduce the number of
false positives and redundant warnings.

@@

\smallstep

\item \textbf{Evaluation.} We applied our tool to \subnum programs 
from 4 different frameworks, comprising \totaloc LOC. The results
show the usefulness of the proposed technique (Section~\ref{sec:evaluation}).
